\documentclass[12pt,a4paper,oneside]{book}
\usepackage{float}
\usepackage{booktabs}
\usepackage{scrextend}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,bm,dsfont}	
\usepackage{amsthm}                         
\usepackage{graphics}                       
\usepackage{graphicx}                       
\usepackage[usenames]{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}  
\usepackage{xr-hyper}              
\usepackage{geometry}                      
\usepackage{rotating}                      
\usepackage{enumerate}
\usepackage{textcomp}
\usepackage{cite}
\usepackage{subcaption}
\usepackage{titlesec}
\usepackage{fancyhdr}
\pagestyle{plain} % Do not print headers
\usepackage{epsfig}
\usepackage[percent]{overpic}
\usepackage{listings}
\usepackage{footmisc}
\usepackage[pdfstartview=FitB,pdfstartpage=1,backref=true]{hyperref}
\hypersetup{
	colorlinks=true,	
	linkcolor={red},
	citecolor={LimeGreen},
	urlcolor={blue}}
\usepackage{makeidx}
\usepackage[nottoc,notlot,notlof]{tocbibind} 
\usepackage{float}
\usepackage{epsfig}
\usepackage[percent]{overpic}
\usepackage{listings}
\usepackage{titlesec}
\usepackage{fancyvrb}
\usepackage{relsize}
\usepackage{textcomp}
\usepackage{threeparttable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Some configurations %%%%%%%%%%%%%%%%%%%%%%%%%%%%



\titleformat{\chapter} % No print chapter headings
{\Large\bfseries} 
{}                
{0pt}             
{\huge}

% define my verbatim environment, requires packages fancyvrb & relsize
\renewcommand{\FancyVerbFormatLine}[1]{\makebox[2mm][l]{}#1}
\DefineVerbatimEnvironment%
{Code}{Verbatim}
{fontsize=\relsize{-1.5},
	samepage=true,
	frame=single}

\newcommand{\codeq}[1]{\code{\textquotesingle{}#1\textquotesingle}}  % requires package textcomp

% define my verbatim environment, requires packages fancyvrb & relsize
\renewcommand{\FancyVerbFormatLine}[1]{\makebox[2mm][l]{}#1}
\DefineVerbatimEnvironment%
{Notice}{Verbatim}
{fontsize=\relsize{-1.5},
	samepage=true,
	xleftmargin=10mm,
	framesep=5mm,
	frame=single}
	
\usepackage{paralist} %for the environment compactitem with less space between items
\let\itemize\compactitem
  \let\enditemize\endcompactitem
  \let\enumerate\compactenum
  \let\endenumerate\endcompactenum
  \let\description\compactdesc
  \let\enddescription\endcompactdesc
  \pltopsep=\medskipamount
  \plitemsep=1pt
  \plparsep=1pt

\setkomafont{labelinglabel}{\normalfont}%{\ttfamily}
\setkomafont{labelingseparator}{\normalfont}
\makeatletter
\renewenvironment{labeling}[2][]{%
  \def\sc@septext{#1}%
  \list{}{\settowidth{\labelwidth}{{%
        \usekomafont{labelinglabel}{#2%
          \usekomafont{labelingseparator}{\sc@septext}}%
      }}%
    \leftmargin\labelwidth \advance\leftmargin by \labelsep
    \let\makelabel\labelinglabel
    \itemsep-4pt% <- Here
  }%
}{%
  \endlist
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%% Some new commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\mpng}[0]{{\tt MPNG}}
\newcommand{\mpgc}[0]{{\tt MPGC}}
\newcommand{\mpngpath}[1]{\textsf{\textsl{{\relsize{-1.0}\textless{}\mbox{MPNG}\textgreater{}}}}\code{{#1}}}
\newcommand{\mpnggitpath}[1]{\textsf{\textsl{{\relsize{-1.0}\textless{}\mbox{\code{E:\textbackslash GITHUB\textbackslash MPNG}}\textgreater{}}}}\code{{#1}}}  
\newcommand{\mpngcasepath}[1]{\textsf{\textsl{{\relsize{-1.0}\textless{}\mbox{MPNG/Cases}\textgreater{}}}}\code{{#1}}} 
\newcommand{\mpngexamplepath}[1]{\textsf{\textsl{{\relsize{-1.0}\textless{}\mbox{MPNG/Examples}\textgreater{}}}}\code{{#1}}}
\newcommand{\mpngurl}[0]{https://github.com/MATPOWER/mpng.git}
\newcommand{\mpngversion}[0]{0.99a}
\newcommand{\matlab}[0]{{\sc Matlab}}
\newcommand{\matpower}[0]{{\sc Matpower}}
\newcommand{\pserc}[0]{{\sc PSerc}}
\newcommand{\doi}[1]{doi:~\href{https://doi.org/#1}{#1}}
\newcommand{\Real}{\mathbb{R}}
\newcommand{\code}[1]{{\relsize{-0.5}{\tt{{#1}}}}}  % requires package relsize
% Note: to get straight single quotes in \code you have to use one of the
%       following: \char13 \char'15 \char"0D \textquotesingle


%%%%%%%%%%%%%%%%%%%%%%%%%%%% Main document  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagenumbering{roman}  
\begin{document}
	\include{Chapters/Front_matter}
	\addtocontents{toc}{\vspace{-4ex}}
	\tableofcontents                            
	\listoffigures
	\listoftables	
	\include{Chapters/Introduction}
	\include{Chapters/Getting_started}
	\include{Chapters/Natural_Gas_Flow}
	\include{Chapters/Formulation}
	\include{Chapters/Examples}
	\include{Chapters/Acknowledgements}
	\part*{Appendix}
	\include{Chapters/Appendixes}	
	
	\clearpage	
	\begin{thebibliography}{99}
	\bibitem{zimmerman2011}
	R.~D. Zimmerman, C.~E. Murillo-S{\'a}nchez, and R.~J. Thomas, ``\matpower{}: Steady-State Operations, Planning and Analysis Tools for Power Systems Research and Education,'' \emph{Power Systems, IEEE Transactions on}, vol.~26, no.~1, pp.~12--19, Feb.~2011.
	\doi{10.1109/TPWRS.2010.2051168}
	
	\bibitem{matpower}
	R.~D. Zimmerman, C.~E. Murillo-S{\'a}nchez (2019). \matpower{}\\~
	[Software]. Available: \url{https://matpower.org}\\
	\doi{10.5281/zenodo.3236535}
	
	\bibitem{bsd}
	The BSD 3-Clause License. [Online]. Available: \url{https://opensource.org/licenses/BSD-3-Clause}.
	
	\bibitem{mpng2019}
	S.~García-Marín, W.~González-Vanegas, and C.~E. Murillo-Sánchez, ``MPNG:\matpower{}-Natural Gas,'' 2019.
	[Online]. Available: \url{\mpngurl}
		
	\bibitem{matpower_manual}
	\matpower{} User's Manual. [Online]. Available: \url{https://matpower.org/doc/manuals/}.	
	
	\bibitem{Woldeyohannes2011}
	Abraham~Debebe Woldeyohannes and Mohd Amin~Abd Majid.
	\newblock Simulation model for natural gas transmission pipeline network
	system.
	\newblock {\em Simulation Modelling Practice and Theory}, 19(1):196--212, 2011.\\
	\doi{10.1016/j.simpat.2010.06.006}	
	
	\bibitem{Osiadacz2001}
	Andrzej~J. Osiadacz and Maciej Chaczykowski.
	\newblock Comparison of isothermal and non-isothermal pipeline gas flow models. 
	\newblock {\em Chemical Engineering Journal}, 81(1):41 -- 51, 2001.\\
	\doi{10.1016/S1385-8947(00)00194-7}	
	
	\bibitem{Banda2006}
	Mapundi~K. Banda, Michael Herty, Axel Klar.
	\newblock Gas flow in pipeline networks.
	\newblock {\em Networks \& Heterogeneous Media}, 1(1): 41 -- 56, 2006.\\
	\doi{10.3934/nhm.2006.1.41} 
	
	\bibitem{Wolf2000}
	Daniel de Wolf and Yves Smeers.
	\newblock The Gas Transmission Problem Solved by an Extension of the Simplex Algorithm.
	\newblock {\em Management Science}, 59(1): 1454 -- 1465, 2000.\\
	\doi{10.1287/mnsc.46.11.1454.12087}
	
	\bibitem{Shabanpour2016}
	Amin Shabanpour-Haghighi and Ali Reza Seifi.
	\newblock Effects of district heating networks on optimal energy flow of multi-carrier systems.
	\newblock {\em Renewable and Sustainable Energy Reviews}, 46(11): 379 -- 387, 2016.\\
	\doi{10.1016/j.rser.2015.12.349}
		
	\bibitem{Chen2017}
	S. Cheng, Z. Wei, G. Sun, K.W. Cheung, Y. Sun.
	\newblock Multi-Linear Probabilistic Energy Flow Analysis of Integrated Electrical and Natural-Gas Systems.
	\newblock {\em IEEE Transactions on Power Systems}, 32(3): 1970 -- 1979, 2017.\\
	\doi{10.1109/TPWRS.2016.2597162}
	
	\bibitem{Midthun2007}
	K. T. Midhunt.
	\newblock Optimization models for liberalized natural gas markets.
	\newblock {\em Norwegian University of Science and Technology, Faculty of Social Science and Technology Management, Department of Sociology	and Political Science}, 2007.	
	
	\bibitem{Cui2016}
	H. Cui., F. Li., Q. Hu., L. Bai., and X. Fang.
	\newblock Day-ahead coordinated operation of utility-scale electricity and natural gas networks considering demand response based virtual power plants.
	\newblock {\em Applied Energy}, 176: 183 -- 195, 2016.\\
	\doi{10.1016/j.apenergy.2016.05.007}
	
    \end{thebibliography}	
\end{document}