\normalsize
\pagenumbering{arabic}
\setcounter{page}{1}

\chapter{Introduction}
\label{chap:intro}

\section{Background}
\label{sec:background}

\mpng{} is a \matpower{}-based~\cite{zimmerman2011,matpower} package for solving optimal power and natural gas flow problems. \mpng{} uses the general user nonlinear constraints capability of \matpower{} to model the gas network taking into account gas-fired power generators, storage units, wells, power-and-gas-driven compressors, and nodes with stratified demand (different market segments get different priorities). The \mpng{} source code can be found at:

\bigskip
~~~~~~~~~~~~~~~~~~~~~~\url{\mpngurl}
\bigskip

\noindent \mpng{} was developed by Sergio~García-Marín~\footnote[1]{ Universidad Nacional de Colombia - sede Manizales.\label{foot:UNAL}} and Wilson~González-Vanegas~\footnote[2]{ Universidad Tecnológica de Pereira.\label{foot:UTP}} under the direction of Professor Carlos~E.~Murillo-S\'anchez~\footref{foot:UNAL}. The initial need for a \matpower{}-based power and natural gas optimal flow package was born out of a project aimed at analyzing the integrated operation of the Colombian power and natural gas systems.\footnote[3]{ Project number 1110-745-58696 funded by Colciencias, Colombia.}

\section{License and Terms of Use}
\label{sec:license}

As a \matpower{}-based package, \mpng{} is distributed under the 3-clause BSD license~\cite{bsd}. The full text of the license can be found in the \code{LICENSE} file at the top level of the distribution or at \url{https://github.com/MATPOWER/mpng/blob/master/LICENSE} and reads as follows. 

\begin{Notice}
Copyright (c) 2019, individual contributors (see AUTHORS file for 
details). All rights reserved.

Redistribution and use in source and binary forms, with or without
modification, are permitted provided that the following conditions
are met:

1. Redistributions of source code must retain the above copyright
notice, this list of conditions and the following disclaimer.

2. Redistributions in binary form must reproduce the above copyright
notice, this list of conditions and the following disclaimer in the
documentation and/or other materials provided with the distribution.

3. Neither the name of the copyright holder nor the names of its
contributors may be used to endorse or promote products derived from
this software without specific prior written permission.

THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
"AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS
FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE
COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT,
INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING,
BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN
ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE
POSSIBILITY OF SUCH DAMAGE.
\end{Notice}

\section{Citing MPNG}
\label{sec:citing_MPNG}

While not required by the terms of the license, we do request that publications derived from the use of \mpng{} explicitly acknowledge that fact by citing this manual~\cite{mpng2019}. In the near future, a journal publication to appear should be cited instead.

\begin{quote}
	\small
	S.~García-Marín, W.~González-Vanegas, and C.~E. Murillo-Sánchez, ``MPNG: \matpower{}-Natural Gas,'' 2019.
	[Online]. Available: \url{\mpngurl}
\end{quote}